Global Climate of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and Spitzer Phase Curve Observations

### 2017-10-29 ms.tex
moel selection

Second, we tested whether the fit rms decreases as expected when the light curve in binned in time.  If the noise is ``white" (uncorrelated in time), the residuals are expected to decrease by a factor of $\sqrt{N}$, where $N$ is the number of points in a bin. Figure\,\ref{fig:rms} shows the binned residuals compared to expectations for white noise. The \HST/WFC3 and \Spitzer\ Channel 2 light curves agree well with expectations, whereas \Spitzer\ Channel 1 shows higher noise than expected as bin size increases. This test confirms the existence of time-correlated noise in the Channel 1 light curve that can be seen by eye in the residuals in Figure\,\ref{fig:phasecurves}. Both \Spitzer\ channels use the same detector, but Channel 1 data are more susceptible to time-correlated noise because the the point spread function is narrower at shorter wavelengths, making intrapixel sensitivity variations more pronounced.

Third, we calculated several goodness of fit statistics. $\chi^2$, AIC, BIC.

@@

\begin{deluxetable}{lllllll}
\tablecolumns{7}
\tablewidth{0pt}:
\tablecaption{Model Comparison \label{table:models}}
\tablehead{
\colhead{Data} & \colhead{Model} & \colhead{$T_\mathrm{min}$} & \colhead{$T_\mathrm{max}$} & \colhead{$\chi^2$} & \colhead{$\Delta_\mathrm{AIC}$} & \colhead{$\Delta_\mathrm{BIC}$}}
\startdata
WFC3 & Harmonics & 1214 & 3251 & 1.5 & 0.0 & 0.0 \\
\, & Kinematic & 1980 & 3958 & 1.6 & 11.8 & 11.8 \\
\, & Two Temp. & 0 & 2887 & 1.6 & 47.7 & 43.2 \\
Ch 1 & Harmonics & 1280 & 3444 & 0.9 & 0.0 & 0.0 \\
\, & Kinematic & 1955 & 3675 & 0.9 & 34.3 & 34.3 \\
\, & Two Temp. & 1429 & 3041 & 0.9 & 10.7 & 17.6 \\
Ch 2 & Harmonics & 902 & 3786 & 1.1 & 0.0 & 3.1 \\
\, & Kinematic & 1703 & 4276 & 1.1 & 14.35 & 17.41 \\
\, & Two Temp. & 1361 & 3311 & 1.1 & 23.9 & 0.0 \\
\enddata
\vspace{-0.8cm}
\tablecomments{comments}
\end{deluxetable}

@@

All of the models provide good fits to the observed phase curves. Table\,\ref{tab:model_comparison} summarized the goodness of fit according to the reduced $\chi^2$, Bayesian information criterion (BIC), and Aikike information criterion (AIC). These metrics for assessing fit quality are . The AIC penalizes model complexity relatively LESS? than the BIC. 
Spherical harmonics provide the best fit most of the time.

>>>>

Second, we tested whether the fit rms decreases as expected when the light curve in binned in time.  If the noise is ``white" (uncorrelated in time), the residuals are expected to decrease by a factor of $\sqrt{N}$, where $N$ is the number of points in a bin. Figure\,\ref{fig:rms} shows the binned residuals compared to expectations for white noise. The \HST/WFC3 and \Spitzer\ Channel 2 light curves agree well with expectations, whereas \Spitzer\ Channel 1 shows higher noise than expected as bin size increases. This test confirms the presence of time-correlated noise in the Channel 1 light curve that can be seen by eye in the residuals in Figure\,\ref{fig:phasecurves}. Both \Spitzer\ channels use the same detector, but Channel 1 data are more susceptible to time-correlated noise because the the point spread function is narrower at shorter wavelengths, making intrapixel sensitivity variations more pronounced.

The reduced $\chi^2$ values for the fits are near unity. FIXME when you have them all.
%Third, we calculated several goodness of fit statistics. $\chi^2$, AIC, BIC.

@@

\begin{deluxetable}{llllll}
	\tablecolumns{6}
	\tablewidth{0pt}:
	\tablecaption{Model Comparison \label{table:model_comparison}}
	\tablehead{
	\colhead{Data} & \colhead{Model} & \colhead{$T_\mathrm{min}$} & \colhead{$T_\mathrm{max}$} & \colhead{$\Delta_\mathrm{AIC}$} & \colhead{$\Delta_\mathrm{BIC}$}}
		\startdata
		WFC3 & Sph. Harmonics & 1214 & 3251 & 0.0 & 0.0 \\
		\, & Kinematic & 1980 & 3958 & 11.8 & 11.8 \\
		\, & Two Temp. & 0 & 2887 & 47.7 & 43.2 \\
		Ch 1 & Sph. Harmonics & 1280 & 3444 & 0.0 & 0.0 \\
		\, & Kinematic & 1955 & 3675 & 34.3 & 34.3 \\
		\, & Two Temp. & 1429 & 3041 & 10.7 & 17.6 \\
		Ch 2 & Sph. Harmonics & 902 & 3786 & 0.0 & 3.1 \\
		\, & Kinematic & 1703 & 4276 & 14.35 & 17.41 \\
		\, & Two Temp. & 1361 & 3311 & 23.9 & 0.0 \\
		\enddata
		\vspace{-0.8cm}
		\tablecomments{comments}
	\end{deluxetable}

@@

All of the models provide reasonable fits to the data, but they yield signficantly different temperature maps. Table\,\ref{tab:model_comparison} lists the minimum and maximum temperatures for the best fit models to the WFC3 broadband and two Spitzer phase curves. We also list the Bayesian information criterion (BIC) and Aikike information criterion (AIC) values for the fits. Both of these statistics are an approximation of the Bayesian evidence for a given model, but the BIC penalizes model complexity relatively more than the AIC \citep{kass95}.

Spherical harmonics generally provide the best fit according to the AIC and BIC.

While the spherical harmonics model generally produces the best fits according to both the BIC and the AIC,
